j_play

### 2020-12-07 scripts/Final_project.Rmd
Final BC table by designation - select years

>>>>

```{r Provincial Data Table}
# A table showing special need designation by year in BC.
need_des <- BCdata %>% 
  janitor::clean_names() %>% 
  select(-c(data_level,
            public_or_independent,
            district_number,
            district_name,
            school_number,
            school_name,
            special_needs_code)) %>% 
  group_by(school_year, special_needs_desc) %>% 
  mutate(number_of_students = sum(number_of_students, na.rm = TRUE)) %>% 
  distinct() %>% 
  pivot_wider(names_from = school_year,
              values_from = number_of_students) %>% 
  select(c("1996/1997",
           "2001/2002",
           "2005/2006",
           "2010/2011",
           "2015/2016",
           "2019/2020")) %>% 
  rename("Special Needs" = special_needs_desc)

apa_table(need_des,
          caption = "Special Needs Designation by Select Years (BC)",
          note = "NAs indicate masked data where students <10")
```

### 2020-12-07 scripts/j_play.Rmd
Final BC table by designation - select years

#unique(count_by_year$school_year)
```

@@

``` {r District Level Population Table}
#Data Prep
census_data <- district_class %>% 
  janitor::clean_names() %>% 
  group_by(district_name, district_number, school_year) %>% 
  mutate(est_students = sum(number_of_students, na.rm = TRUE)) %>% 
  select(-c("school_year",
            "data_level",
            "public_or_independent",
            "special_needs_code",
            "number_of_students")) %>% 
  distinct()

#Table
apa_table(
  census_data,
    digits = 0,
  caption = "District Classification by Population According to 2016 Census",
  note = "Number of students does not include masked data.",
  col.names = c("District Number",
            "District Name",
            "Population",
            "Classification",
            "Number of Students")
)

>>>>

#unique(count_by_year$school_year)

# A table showing special need designation by year in BC.
need_des <- BCdata %>% 
  janitor::clean_names() %>% 
  select(-c(data_level,
            public_or_independent,
            district_number,
            district_name,
            school_number,
            school_name,
            special_needs_code)) %>% 
  group_by(school_year, special_needs_desc) %>% 
  mutate(number_of_students = sum(number_of_students, na.rm = TRUE)) %>% 
  distinct() %>% 
  pivot_wider(names_from = school_year,
              values_from = number_of_students) %>% 
  select(c("1996/1997",
           "2001/2002",
           "2005/2006",
           "2010/2011",
           "2015/2016",
           "2019/2020")) %>% 
  rename("Special Needs" = special_needs_desc)

apa_table(need_des,
          caption = "Special Needs Designation by Select Years (BC)",
          note = "NAs indicate masked data where students <10")

as_tibble(BCdata)
```

@@

``` {r District Level Population Table}
#Data Prep
#census_data <- district_class %>% 
 # janitor::clean_names() %>% 
  #group_by(district_name, district_number, school_year) %>% 
  #mutate(est_students = sum(number_of_students, na.rm = TRUE)) %>% 
  #select(-c("school_year",
  #          "data_level",
   #         "public_or_independent",
    #        "special_needs_code",
     #       "number_of_students")) %>% 
  #distinct()

#Table
#apa_table(
#  census_data,
#    digits = 0,
#  caption = "District Classification by Population According to 2016 Census",
#  note = "Number of students does not include masked data.",
#  col.names = c("District Number",
#            "District Name",
#            "Population",
#            "Classification",
#            "Number of Students")
#)
